Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/eval.tex
Update on Overleaf.

The inner-product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. Inner-product involves multiplying two matrices by taking dot products of corresponding rows and columns, while outer-product computes the product of all pairs of elements from the input matrices. Further explanation is available in Section 2.2 of  ~\cite{zhang2021gamma}.

Figures \ref{fig:spgemm_small} and \ref{fig:spgemm_large} illustrate SpGEMM results with Finch and TACO. Notably, inner-product can be very inefficient unless sparse matrices are nearly dense due to the cost of intersections incurring redundant traversals. Additionally, TACO does not support outer product due to its lack of support for scatter into a 2D workspace, limiting its use for large sparse matrices. In contrast, Finch supports scatter into 2D workspace, allowing for comparison with Gustavson's algorithm for large sparse matrices.

>>>>

The inner-product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. Inner-product involves multiplying two matrices by taking dot products of corresponding rows and columns, while outer-product computes the product of all pairs of elements from the input matrices.
Gustavson's algorithm computes the output matrix one row at a time, by scaling and merging rows of the second sparse matrix corresponding to the nonzero columns of a row of the first sparse matrix.
Further explanation is available in Section 2.2 of  ~\cite{zhang2021gamma}.

Figures \ref{fig:spgemm_small} and \ref{fig:spgemm_large} illustrate SpGEMM results with Finch and TACO. Notably, inner-product can be very inefficient unless sparse matrices are nearly dense due to the cost of intersections incurring redundant traversals. Additionally, TACO only supports outer product when the output matrix format is dense. It does not support outer product due to its lack of support for scatter into a 2D workspace, limiting its use for large sparse matrices. In contrast, Finch supports scatter into 2D workspace, allowing for comparison with Gustavson's algorithm for large sparse matrices.
